Improving instance-level constrained clustering through Dual Iterated Local Search

### 2019-02-07 Papers/DILS/paperDILS.tex
Añadidos algoritmos TFG, resultados TFG y modificado paper SHADE

\usepackage{lineno,hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{chngpage}
\usepackage{setspace}
\usepackage{amsfonts}
\usepackage[ruled, lined, onelanguage, linesnumbered]{algorithm2e}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newcommand{\myfloatalign}{\centering}
\modulolinenumbers[5]

@@

With the local search defined in this way, it is easy to see that the solution achieved will be the optimal local $s^*$ closest to the initial solution $s$.

\textcolor{red}{Poner un dibujo que lo ejemplifique}

@@

With ILS, once we have reached a local optimum $s^*$, we apply a perturbation to it that, with a high probability, will result in a new solution $s^prime$ that will not be a local optimum and will be far enough away from $s^*$. After that, we will apply the simple local search method to find a new local optimal $s^{*\prime}$.

\textcolor{red}{Poner un dibujo que lo ejemplifique, el del handbook of MH pag 368}

It should be noted that, if the disturbance applied to $s*$ is too small, the most likely is that the local optimum closest to $s^prime$ is $s*$ and therefore the solution space will not be explored effectively. On the other hand, if the disturbance is too big, there will be no bias in the generation of new solutions, and therefore the procedure becomes a random reboot-type method.

>>>>

%\usepackage{pdfpages}
\usepackage{graphics, graphicx, float, url}
\usepackage{lineno,hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{chngpage}
\usepackage{setspace}
\usepackage{amsfonts}
\usepackage[ruled, lined, onelanguage, linesnumbered]{algorithm2e}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newcommand{\myfloatalign}{\centering}
\modulolinenumbers[5]

\usepackage{epstopdf}
\epstopdfDeclareGraphicsRule{.tiff}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tiff}

@@

With the local search defined in this way, it is easy to see that the solution achieved will be the optimal local $s^*$ closest to the initial solution $s$. Figure \ref{img:LS} shows a pictorical representation of the above.

\begin{figure}[!h]
	\centering
	\includegraphics[scale=0.25]{Figures/LS.png}
	\caption{Local optimum achieved by a local search procedure}\label{img:LS}
\end{figure}

@@

With ILS, once we have reached a local optimum $s^*$, we apply a perturbation to it that, with a high probability, will result in a new solution $s^\prime$ that will not be a local optimum and will be far enough away from $s^*$. After that, we will apply a local search procedure to find a new local optimal $s^{*\prime}$. Figure \ref{img:ILS} shows a representation of the above concepts.

\begin{figure}[!h]
	\centering
	\includegraphics[scale=0.25]{Figures/ILS.png}
	\caption{No se como llamar a esta puta imagen}\label{img:ILS}
\end{figure}

It should be noted that, if the disturbance applied to $s*$ is too small, the most likely is that the local optimum closest to $s^\prime$ is $s^*$ and therefore the solution space will not be explored effectively. On the other hand, if the disturbance is too big, there will be no bias in the generation of new solutions, and therefore the procedure becomes a random reboot-type method.
